Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-29 ms.tex
added W2 SGC figure

@@

\begin{figure}
 \begin{center}
  \epsfig{file=w1_image_noise.eps, width=3.0in}
  \caption{\label{fig:image_noise} Illustration of reduced image noise
           in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
           at ($\alpha$, $\delta$) = (335.4585$^{\circ}$, $-$10.5801$^{\circ}$). 
           This is a representative location at low ecliptic latitude and high 
           Galactic latitude,  with $\sim$2$\times$ as much coverage in our 
           AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
           images are rendered with identical color stretches.}
 \end{center}
\end{figure}

Given that we imposed various cuts to eliminate time-dependent artifacts,
it is reasonable to ask whether we have created any zero-coverage holes
as a result. We have checked all 18,240 of our integer coverage maps, and find
that every pixel has $\ge$18 epochs in W1 and $\ge$15 epochs in W2.

@@

>>>>

\begin{figure*} [ht]
 \begin{center}
  \epsfig{file=w2_large_scale.eps, width=7.0in}
  \caption{\label{fig:w2_large} A large portion of the south Galactic
           cap near the ecliptic plane is shown in W2. Top: \cite{lang14}
           unWISE coadds based on the AllWISE release imaging and without
           rejection of Moon-contaminated frames. Bottom: same region of
           sky in our new AllWISE+NEOWISER stacks, with double the
           redundancy in sky coverage and rejection/recovery of 
           Moon-contaminated frames.}
 \end{center}
\end{figure*}
% should state approximate bounding coords in terms of lambda, beta

@@

\begin{figure}[ht]
 \begin{center}
  \epsfig{file=w1_image_noise.eps, width=3.0in}
  \caption{\label{fig:image_noise} Illustration of reduced image noise
           in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
           at ($\alpha$, $\delta$) = (335.4585$^{\circ}$, $-$10.5801$^{\circ}$). 
           This is a representative location at low ecliptic latitude and high 
           Galactic latitude,  with $\sim$2$\times$ as much coverage in our 
           AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
           images are rendered with identical color stretches.}
 \end{center}
\end{figure}

Given that we imposed various frame-level cuts to eliminate time-dependent 
artifacts, it is reasonable to ask whether we have created any zero-coverage 
holes as a result. We have checked all 18,240 of our integer coverage maps, and
find that every pixel has $\ge$18 epochs in W1 and $\ge$15 epochs in W2.

@@

% could list future improvement's i'd like to implement for NEO(2+) coadds
% for instance masking of bright star ghosts and correction
% of bright star scattered light, possibly creation of a bitmask output
% like that of meisner/finkbeiner dust coadds
% also min/max removal step as added protection against outliers
